Title

### 2013-03-18 inc/hardware/introduction.tex
added some text the the hardware introduction

>>>>

In Chapters \ref{chap:previous_models} through \ref{chap:model_results}, I have explored the mathematical side of designing an ultrafast electron microscope; modeling the behavior of a pulse and the effect that column elements have upon it.
However, microscopy is an experimental science, and designing a UEM is no less hands-on.

It is our belief that a successful UEM project cannot simply stem from small modifications to the platform of a conventional electron microscope.
In this chapter I describe the prototype UEM system that is being built at UIC.
By necessity much of it is custom built, specifically designed to either allow flexibility or to meet some technical challenge.
